Geometric Signs on Paleolithic Mobile Objects as Cultural Group Markers

### 2025-02-08 endofquarterpaper.qmd
experimentation
new-groups

```{r}
groups <- list("1" = c("Abri Pataud", "El Rascaño", 
                         "Fumane", "La Viña",
                         "Lhotka", "Pod Hradem",
                         "Riparo Bombrini", "Sirgenstein Cave"),
                "2" = c("Kvasice", "Labeko Koba", 
                        "Les Rois", "Slatinice",
                        "Göpfelsteinhöhle"),
                "3" = c("Aurignac", "d'Engihoul",
                         "Istállóskő Cave", "Hohlenstein-Stadel",
                         "Gargas", "Grotte de la Verpillière I", 
                         "Mladeč", "Brassempouy",
                         "Gatzarria"),
                "4" = c("Wildscheuer", "Breitenbach",
                        "Peskő Cave", "Vindija Cave",
                        "El Castillo"),
                "5" = c("Trou Magrite",
                        "Grotte de Goyet", "Bockstein-Törle"),
                "6" = c("Trou al'Wesse", "Maisières-Canal",
                        "Les Cottés", "Le Terme Pialat"),
                "7" = c("Vogelherd","Hohle Fels",
                        "Geissenklösterle"),
               "8" = c("Tuto de Camalhot","Abri Lartet/Gorge d'Enfer",
                        "Castanet", "Le Trou Du Renard", 
                        "Grottes de Fonds-de-Forêt" ),
               "9" = c("Nová Dědina", "Menton/Grottes du Grimaldi",
                        "Grotte du Renne", "Solutré", 
                        "Žlutava", "Spy"),
                "10" = c("Cellier", "Blanchard", 
                         "La Ferrassie", "Hornos de la Pena",
                         "Otaslavice"),
                "11" = c("La Souquette", "Shelter Birów IV",
                         "Abri de Laussel", "Abri du Poisson"))
group_df <- 
  enframe(groups, 
          name = "group", 
          value = "site_name") %>%
  unnest(cols = site_name)

@@

# Load required libraries
library(ggplot2)

@@

# get country names, for example
x_df <- 
  artifact_data %>% 
  rownames_to_column("site_name") %>% 
  left_join(signbase_full_clean %>% 
              distinct(site_name, .keep_all = TRUE) %>% 
              select(site_name,
                     country),
            by = "site_name")

countries <- x_df$country

@@

ggraph(disim_net, layout="fr") +
  geom_edge_link(aes(width = weight, 
                     alpha=weight), 
                 edge_colour = "black", 
                 show.legend=T) +
  scale_edge_width(range=c(0.5,1.5)) +
  scale_edge_colour_gradient(low = "#CCCCCC",
                             high = "#000000") +
  geom_node_point(alpha=1, size=5) +
  geom_node_text(aes(label=row.names(artifact_data)), 
                 size=6, 
                 family= "Arial", 
                 repel=T) +
  theme(text= element_text(size = 15), 
        panel.background = element_rect(fill = 'white'))
```

>>>>

```{r}
groups <- list("1" = c("Abri Pataud", "El Rascaño", 
                       "Fumane", "La Viña",
                       "Lhotka", "Pod Hradem",
                       "Riparo Bombrini", "Sirgenstein Cave"),
               "2" = c("Aurignac", "Gargas",
                       "Grotte de la Verpillière I","Hohlenstein-Stadel",
                       "Istállóskő Cave", "Mladeč",
                       "d'Engihoul"),
               "3" = c("Breitenbach", "Peskő Cave",
                       "Vindija Cave", "Wildscheuer"),
               "4" = c("Kvasice", "Labeko Koba", 
                       "Les Rois"),
               "5" = c("Le Trou Du Renard", "Abri Lartet/Gorge d'Enfer",
                       "Tuto de Camalhot", "Castanet", 
                       "Gatzarria", "Abri du Poisson"),
               "6" = c("Bockstein-Törle", "Grotte de Goyet",
                        "Trou Magrite", "Brassempouy"),
               "7" = c( "Göpfelsteinhöhle",  "Slatinice", 
                        "Grotte du Renne"),
               "8" = c( "El Castillo", "Trou al'Wesse", 
                        "Maisières-Canal"),
               "9" = c("Vogelherd","Hohle Fels",
                       "Geissenklösterle", "Le Terme Pialat", 
                       "Les Cottés", "Spy",  "Grottes de Fonds-de-Forêt"),
               "10" = c("Nová Dědina", "Menton/Grottes du Grimaldi",
                        "Solutré", "Žlutava", 
                        "Hornos de la Pena", "Otaslavice"),
               "11" = c("Cellier", "Blanchard", 
                        "La Ferrassie"),
               "12" = c("La Souquette", "Shelter Birów IV",
                        "Abri de Laussel"))
group_df <- 
  enframe(groups, 
          name = "group", 
          value = "site_name") %>%
  unnest(cols = site_name)

@@

@@

# get country names, for example
x_df <- 
  artifact_data %>% 
  rownames_to_column("site_name") %>% 
  left_join(signbase_unique_groups %>% 
              select(site_name,
                     group),
            by = "site_name")

countries <- x_df$group

@@

ggraph(disim_net, layout="fr") +
  geom_edge_link(aes(width = weight, 
                     alpha=weight), 
                 edge_colour = "black", 
                 show.legend=T) +
  scale_edge_width(range=c(0.5,1.5)) +
  scale_edge_colour_gradient(low = "#CCCCCC",
                             high = "#000000") +
  geom_node_point(alpha=1, size=5) +
  geom_node_text(aes(label=row.names(artifact_data)), 
                 size=6, 
                 family= "Arial", 
                 repel=T, max.overlaps = 100) +
  theme(text= element_text(size = 15), 
        panel.background = element_rect(fill = 'white'))
```
